### 2020-12-01 R - Deliverable/MSDS 6371 - Project.Rmd
Initial Commit

---
title: "stats-project"
author: "David Grijalva & Ricco Ferraro"
date: "11/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(olsrr)
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(car)
library(data.table)
library(mltools)
```

```{r message=FALSE, warning=FALSE}
data = read_csv("../Data/train.csv")
data
#Convert <chr> to <fctr>
data = as.data.frame(unclass(data))
data
```

```{r message=FALSE, warning=FALSE}

# Select relevant columns and Neighborhood
train_data_q1 = data %>% select(Id, GrLivArea, Neighborhood, SalePrice ) %>% filter(Neighborhood == "NAmes" | Neighborhood ==  "Edwards" | Neighborhood ==  "BrkSide") %>% droplevels()
train_data_q1
train_data_q2 = data %>% select(Id, GrLivArea, Neighborhood, SalePrice ) 
train_data_q2
```

Question of interest
Is the square footage of the living area and the neighborhood  related to the house sales price
neighborhood: NAmes, Edwards and BrkSide 
Note:  For living area provide results in increments of 100 sq. ft.

```{r message=FALSE, warning=FALSE}
# Create scatter plot graphing function

scatter_func = function (data, i){
  title = paste("SalePrice vs GrLivArea by Neighborhood:", i)
  figure = data %>%  filter (Neighborhood==i) %>%  ggplot(aes(x=GrLivArea, y= SalePrice)) + geom_point() + scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +  geom_smooth(formlula="lm") + ggtitle(paste0(title))
return (figure)
}

hist_boxplot = function (data) {
  g1 = data %>% ggplot() + geom_histogram(aes(x=SalePrice), fill="steelblue") + scale_x_continuous(labels = function(x) format(x, scientific = FALSE)) + ggtitle("Histogram of Sale Price")
  g2 = data %>% ggplot() + geom_histogram(aes(x=GrLivArea), fill="steelblue") + scale_x_continuous(labels = function(x) format(x, scientific = FALSE)) + ggtitle("Histogram of Square Footage of the Living Area")
  g3 = data %>% ggplot() + geom_boxplot(aes(x=Neighborhood, y=SalePrice, fill=Neighborhood)) + scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) + ggtitle("Boxplot of Sale Price by Neighborhood") +  
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 6 ))
  figure =  ggarrange(g1, g2, g3, ncol=1)
  return(figure)
}

press = function (model) {
  pr = resid(lm_fit_q1)/(1 - lm.influence(lm_fit_q1)$hat)
  return(sum(pr^2))
}

```

```{r fig.height=5, fig.width=5, message=FALSE, warning=FALSE}
hist_boxplot(train_data_q1)
hist_boxplot(train_data_q2)
```

```{r message=FALSE, warning=FALSE}
for (i in unlist(unique(data$Neighborhood)) ) {
  print(scatter_func(data, i))
}

```
#	ANALYSIS 1
```{r message=FALSE, warning=FALSE}
# One hot encode data
#one_encode_train_data_q1 =  one_hot(as.data.table(train_data_q1, dropUnusedLevels=TRUE))

#Complete Fit
# Neighborhood reference: Neighborhood_BrkSide
#lm_fit_q1 = lm(SalePrice ~. -Id-Neighborhood_BrkSide, data = one_encode_train_data_q1)

lm_fit_q1 = lm(SalePrice ~. -Id, data = train_data_q1)

press(lm_fit_q1)

summary(lm_fit_q1)
confint(lm_fit_q1,  level=0.995)

```

```{r message=FALSE, warning=FALSE}

RSS = c(crossprod(lm_fit_q1$residuals))
MSE = RSS / length(lm_fit_q1$residuals)
RMSE = sqrt(MSE)
RMSE

g1 = ggplot() + geom_histogram(aes(x=lm_fit_q1$residuals)) + ggtitle("Residuals Histogram")
g2 = ggplot(lm_fit_q1,aes(sample=lm_fit_q1$residuals)) + geom_qq() + geom_qq_line()  + ggtitle("Residuals QQ Plot")
g3 = ggplot(lm_fit_q1, aes(x=lm_fit_q1$fitted.values, y= lm_fit_q1$residuals)) + geom_point() +  geom_hline(yintercept=0) + xlab( "Predicted Value") + ylab("Residual") +  ggtitle("Residuals vs Predicted")
figure =  ggarrange(g1, g2, g3, ncol=3)
figure

# https://www.statmethods.net/stats/rdiagnostics.html

# Influence plot
influencePlot(lm_fit_q1, id.method="identify", main="Influence Plot", sub="Circle size is proportial to Cook's Distance" )

# Cook's D plot
cutoff = 4/((nrow(one_encode_train_data_q1)-length(lm_fit_q1$coefficients)-2))
plot(lm_fit_q1, which=4, cook.levels=cutoff)

#Durbin Watson Test for Colliniarity
durbinWatsonTest(lm_fit_q1)

# Outlier test
outlierTest(lm_fit_q1) # Bonferonni p-value for most extreme obs

# Multi-collinearity variance inflation factors
vif(lm_fit_q1)

```

#	ANALYSIS 2
```{r message=FALSE, warning=FALSE}
# One hot encode data
one_encode_train_data_q2 =  one_hot(as.data.table(train_data_q2, dropUnusedLevels=TRUE))
one_encode_train_data_q2
# Neighborhood reference: Neighborhood_NAmes
lm_fit_q2 = lm(SalePrice ~. -Id -Neighborhood_NAmes, data = one_encode_train_data_q2)
summary(lm_fit_q2)
confint(lm_fit_q2,  level=0.995)
```
## Model Selection
### Stepwise
```{r message=FALSE, warning=FALSE}
#Stepwise Selection
stepwise_fit = ols_step_both_p(lm_fit_q2, pent =0.05, prem=0.05,  details = F)
stepwise_fit

```

```{r message=FALSE, warning=FALSE}
#Forward Selection
fw_fit = ols_step_forward_p(lm_fit_q2, penter=0.05, details = F)
fw_fit
```

```{r message=FALSE, warning=FALSE}
#Backward Selection
bw_fit = ols_step_backward_p(lm_fit_q2, penter=0.05, details = F)
bw_fit

```

```{r message=FALSE, warning=FALSE}

RSS = c(crossprod(lm_fit_q2$residuals))
MSE = RSS / length(lm_fit_q2$residuals)
RMSE = sqrt(MSE)
RMSE

g1 = ggplot() + geom_histogram(aes(x=lm_fit_q2$residuals)) + ggtitle("Residuals Histogram")
g2 = ggplot(lm_fit_q2,aes(sample=lm_fit_q2$residuals)) + geom_qq() + geom_qq_line()  + ggtitle("Residuals QQ Pl0t")
g3 = ggplot(lm_fit_q2, aes(x=lm_fit_q2$fitted.values, y= lm_fit_q2$residuals)) + geom_point() +  geom_hline(yintercept=0) + xlab( "Predicted Value") + ylab("Residual") +  ggtitle("Residuals vs Predicted")
figure =  ggarrange(g1, g2, g3, ncol=3)
figure

# https://www.statmethods.net/stats/rdiagnostics.html

# Influence plot
influencePlot(lm_fit_q2, id.method="identify", main="Influence Plot", sub="Circle size is proportial to Cook's Distance" )

# Cook's D plot
cutoff = 4/((nrow(one_encode_train_data_q2)-length(lm_fit_q2$coefficients)-2))
plot(lm_fit_q2, which=4, cook.levels=cutoff)

#Durbin Watson Test for Colliniarity
durbinWatsonTest(lm_fit_q2)

# Outlier test
outlierTest(lm_fit_q2) # Bonferonni p-value for most extreme obs

# Multi-collinearity variance inflation factors
vif(lm_fit_q2)

```

```

### 2020-12-02 R - Deliverable/MSDS 6371 - Project.Rmd
some changes

@@
 library(mltools)
+
+# options
+#options(scipen = 999)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-data = read_csv("../Data/train.csv")
-data
+data_train= read_csv("../Data/train.csv")
+data_test = read_csv("../Data/test.csv")
 #Convert <chr> to <fctr>
-data = as.data.frame(unclass(data))
-data
+data_train = as.data.frame(unclass(data_train))
+data_test = as.data.frame(unclass(data_test))
+data_test
 ```
@@
 # Select relevant columns and Neighborhood
-train_data_q1 = data %>% select(Id, GrLivArea, Neighborhood, SalePrice ) %>% filter(Neighborhood == "NAmes" | Neighborhood ==  "Edwards" | Neighborhood ==  "BrkSide") %>% droplevels()
+train_data_q1 = data_train %>% select(Id, GrLivArea, Neighborhood, SalePrice ) %>% filter(Neighborhood == "NAmes" | Neighborhood ==  "Edwards" | Neighborhood ==  "BrkSide") %>% droplevels()
+test_data_q1 = data_test  %>% select(Id, GrLivArea, Neighborhood ) %>% filter(Neighborhood == "NAmes" | Neighborhood ==  "Edwards" | Neighborhood ==  "BrkSide") %>% droplevels()
 train_data_q1
-train_data_q2 = data %>% select(Id, GrLivArea, Neighborhood, SalePrice ) 
-train_data_q2
+train_data_q2 = data_train %>% select(Id, GrLivArea, Neighborhood, SalePrice ) 
+train_data_q2$GrLivArea2 = train_data_q2$GrLivArea^2
+
+test_data_q2 = data_test %>% select(Id, GrLivArea, Neighborhood ) 
+test_data_q2$GrLivArea2 = test_data_q2$GrLivArea^2
+
+```
+
+```{r}
+
+lm_fit_experiment = lm(SalePrice ~.
+-Id-Utilities-Street-PoolQC-MiscFeature-Alley-Fence-FireplaceQu-LotFrontage-GarageCond-GarageFinish-GarageQual-GarageType-GarageYrBlt-BsmtExposure-BsmtFinType2-BsmtCond-BsmtFinType1-BsmtQual-MasVnrArea-MasVnrType-Electrical  , data = train)
+lm_fit_experiment
+#Neighborhood_Blmngtn
+
+summary(lm_fit_experiment)
+#confint(lm_fit_experiment,  level=0.995)
+
 ```
@@
 press = function (model) {
-  pr = resid(lm_fit_q1)/(1 - lm.influence(lm_fit_q1)$hat)
+  pr = resid(model)/(1 - lm.influence(model)$hat)
   return(sum(pr^2))
@@
 ```{r message=FALSE, warning=FALSE}
-# One hot encode data
-#one_encode_train_data_q1 =  one_hot(as.data.table(train_data_q1, dropUnusedLevels=TRUE))
+one_encode_train_data_q1 =  one_hot(as.data.table(train_data_q1, dropUnusedLevels=TRUE))
 
-#Complete Fit
-# Neighborhood reference: Neighborhood_BrkSide
-#lm_fit_q1 = lm(SalePrice ~. -Id-Neighborhood_BrkSide, data = one_encode_train_data_q1)
-
-lm_fit_q1 = lm(SalePrice ~. -Id, data = train_data_q1)
+#Reference Neighborhood_BrkSide
+lm_fit_q1 = lm(SalePrice ~. -Id-Neighborhood_BrkSide+Neighborhood_Edwards*GrLivArea+Neighborhood_NAmes*GrLivArea, data = one_encode_train_data_q1)
 
 press(lm_fit_q1)
+ols_press(lm_fit_q1)
 
@@
 
+ols_plot_cooksd_bar(lm_fit_q1)
+ols_plot_dffits(lm_fit_q1)
+ols_plot_diagnostics(lm_fit_q1)
+
+ols_plot_resid_fit(lm_fit_q1)
+ols_plot_resid_pot(lm_fit_q1)
+ols_pred_rsq(lm_fit_q1)
+plot(lm_fit_q1)
 ```
 
-```{r message=FALSE, warning=FALSE}
-
-RSS = c(crossprod(lm_fit_q1$residuals))
-MSE = RSS / length(lm_fit_q1$residuals)
-RMSE = sqrt(MSE)
-RMSE
-
-g1 = ggplot() + geom_histogram(aes(x=lm_fit_q1$residuals)) + ggtitle("Residuals Histogram")
-g2 = ggplot(lm_fit_q1,aes(sample=lm_fit_q1$residuals)) + geom_qq() + geom_qq_line()  + ggtitle("Residuals QQ Plot")
-g3 = ggplot(lm_fit_q1, aes(x=lm_fit_q1$fitted.values, y= lm_fit_q1$residuals)) + geom_point() +  geom_hline(yintercept=0) + xlab( "Predicted Value") + ylab("Residual") +  ggtitle("Residuals vs Predicted")
-figure =  ggarrange(g1, g2, g3, ncol=3)
-figure
-
-# https://www.statmethods.net/stats/rdiagnostics.html
-
-# Influence plot
-influencePlot(lm_fit_q1, id.method="identify", main="Influence Plot", sub="Circle size is proportial to Cook's Distance" )
-
-# Cook's D plot
-cutoff = 4/((nrow(one_encode_train_data_q1)-length(lm_fit_q1$coefficients)-2))
-plot(lm_fit_q1, which=4, cook.levels=cutoff)
-
-#Durbin Watson Test for Colliniarity
-durbinWatsonTest(lm_fit_q1)
-
-# Outlier test
-outlierTest(lm_fit_q1) # Bonferonni p-value for most extreme obs
-
-# Multi-collinearity variance inflation factors
-vif(lm_fit_q1)
+```{r}
+lm_fit_q1$residuals
 
@@
 ```{r message=FALSE, warning=FALSE}
-# One hot encode data
+
 one_encode_train_data_q2 =  one_hot(as.data.table(train_data_q2, dropUnusedLevels=TRUE))
-one_encode_train_data_q2
-# Neighborhood reference: Neighborhood_NAmes
-lm_fit_q2 = lm(SalePrice ~. -Id -Neighborhood_NAmes, data = one_encode_train_data_q2)
+#lm_fit_q2 = lm(SalePrice ~. -Id-Neighborhood_BrkSide, data = one_encode_train_data_q2)
+
+#Neighborhood_Blmngtn
+
+lm_fit_q2 = lm(SalePrice ~.
+-Id-Neighborhood_Blmngtn+(Neighborhood_BrkSide*GrLivArea+Neighborhood_Blueste+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker)*GrLivArea+(Neighborhood_BrkSide+Neighborhood_Blueste+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker)*GrLivArea2, data = one_encode_train_data_q2)
+
 summary(lm_fit_q2)
@@
 stepwise_fit
+stepwise_model = stepwise_fit$model
+ols_press(stepwise_model)
+stepwise_model
+summary(stepwise_model)
+confint(stepwise_model)
 
+ols_plot_cooksd_bar(stepwise_model)
+
+stepwise_model_outliers = ols_plot_cooksd_bar(stepwise_model, print_plot=F)
+stepwise_model_outliers
+
+ols_plot_dffits(stepwise_model)
+ols_plot_diagnostics(stepwise_model)
+
+ols_plot_resid_fit(stepwise_model)
+ols_plot_resid_pot(stepwise_model)
+ols_pred_rsq(stepwise_model)
+plot(stepwise_fit)
 ```
@@
 fw_fit
+fw_model = fw_fit$model
+ols_press(fw_model)
+fw_model
+summary(fw_model)
+confint(fw_model)
+
+ols_plot_cooksd_bar(fw_model)
+
+fw_model_outliers = ols_plot_cooksd_bar(fw_model, print_plot=F)
+fw_model_outliers
+
+ols_plot_dffits(fw_model)
+ols_plot_diagnostics(fw_model)
+
+ols_plot_resid_fit(fw_model)
+ols_plot_resid_pot(fw_model)
+ols_pred_rsq(fw_model)
+plot(fw_fit)
 ```
@@
 bw_fit
+bw_model = bw_fit$model
+ols_press(bw_model)
+bw_model
+summary(bw_model)
+confint(bw_model)
+
+ols_plot_cooksd_bar(bw_model)
+
+bw_model_outliers = ols_plot_cooksd_bar(bw_model, print_plot=F)
+bw_model_outliers
+
+ols_plot_dffits(bw_model)
+ols_plot_diagnostics(bw_model)
+
+ols_plot_resid_fit(bw_model)
+ols_plot_resid_pot(bw_model)
+ols_pred_rsq(bw_model)
+plot(bw_fit)
 
 ```
-
-```{r message=FALSE, warning=FALSE}
-
-RSS = c(crossprod(lm_fit_q2$residuals))
-MSE = RSS / length(lm_fit_q2$residuals)
-RMSE = sqrt(MSE)
-RMSE
-
-g1 = ggplot() + geom_histogram(aes(x=lm_fit_q2$residuals)) + ggtitle("Residuals Histogram")
-g2 = ggplot(lm_fit_q2,aes(sample=lm_fit_q2$residuals)) + geom_qq() + geom_qq_line()  + ggtitle("Residuals QQ Pl0t")
-g3 = ggplot(lm_fit_q2, aes(x=lm_fit_q2$fitted.values, y= lm_fit_q2$residuals)) + geom_point() +  geom_hline(yintercept=0) + xlab( "Predicted Value") + ylab("Residual") +  ggtitle("Residuals vs Predicted")
-figure =  ggarrange(g1, g2, g3, ncol=3)
-figure
-
-# https://www.statmethods.net/stats/rdiagnostics.html
-
-# Influence plot
-influencePlot(lm_fit_q2, id.method="identify", main="Influence Plot", sub="Circle size is proportial to Cook's Distance" )
-
-# Cook's D plot
-cutoff = 4/((nrow(one_encode_train_data_q2)-length(lm_fit_q2$coefficients)-2))
-plot(lm_fit_q2, which=4, cook.levels=cutoff)
-
-#Durbin Watson Test for Colliniarity
-durbinWatsonTest(lm_fit_q2)
-
-# Outlier test
-outlierTest(lm_fit_q2) # Bonferonni p-value for most extreme obs
-
-# Multi-collinearity variance inflation factors
-vif(lm_fit_q2)
-
-```
-
-```

### 2020-12-03 R - Deliverable/MSDS 6371 - Project.Rmd
some changes

@@
 library(mltools)
+library(olsrr)
 
@@
 data_test = as.data.frame(unclass(data_test))
-data_test
+nrow(data_test)
 ```
@@
 test_data_q2$GrLivArea2 = test_data_q2$GrLivArea^2
-
+nrow(test_data_q2)
 ```
@@
 
-lm_fit_experiment = lm(SalePrice ~.
+#lm_fit_experiment = lm(SalePrice ~.
 -Id-Utilities-Street-PoolQC-MiscFeature-Alley-Fence-FireplaceQu-LotFrontage-GarageCond-GarageFinish-GarageQual-GarageType-GarageYrBlt-BsmtExposure-BsmtFinType2-BsmtCond-BsmtFinType1-BsmtQual-MasVnrArea-MasVnrType-Electrical  , data = train)
-lm_fit_experiment
+#lm_fit_experiment
 #Neighborhood_Blmngtn
@@
 
-```{r}
-lm_fit_q1$residuals
-
-```
-
 #	ANALYSIS 2
@@
 one_encode_train_data_q2 =  one_hot(as.data.table(train_data_q2, dropUnusedLevels=TRUE))
+one_encode_test_data_q2 =  one_hot(as.data.table(test_data_q2, dropUnusedLevels=TRUE))
 #lm_fit_q2 = lm(SalePrice ~. -Id-Neighborhood_BrkSide, data = one_encode_train_data_q2)
@@
 
-lm_fit_q2 = lm(SalePrice ~.
--Id-Neighborhood_Blmngtn+(Neighborhood_BrkSide*GrLivArea+Neighborhood_Blueste+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker)*GrLivArea+(Neighborhood_BrkSide+Neighborhood_Blueste+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker)*GrLivArea2, data = one_encode_train_data_q2)
+lm_fit_q2 = lm(SalePrice ~.-GrLivArea2 -Id-Neighborhood_BrkSide+(Neighborhood_Blmngtn+Neighborhood_Blueste+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker)*GrLivArea, data = one_encode_train_data_q2)
 
@@
 #Stepwise Selection
-stepwise_fit = ols_step_both_p(lm_fit_q2, pent =0.05, prem=0.05,  details = F)
+stepwise_fit = ols_step_both_p(lm_fit_q2, pent =0.05, prem=0.05)
 stepwise_fit
+```
+```{r}
+stepwise_fit$predictors
+```
+
+```{r}
 stepwise_model = stepwise_fit$model
 ols_press(stepwise_model)
-stepwise_model
 summary(stepwise_model)
@@
 
+```
+
+```{r}
 ols_plot_cooksd_bar(stepwise_model)
@@
 
+```{r}
+
+stepwise_predictions = c(predict(stepwise_model, newdata = one_encode_test_data_q2))
+
+stepwise_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=stepwise_predictions)
+stepwise_submission
+write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")
+```
+
 ```{r message=FALSE, warning=FALSE}
@@
 fw_fit
+
+```
+
+```{r}
 fw_model = fw_fit$model
 ols_press(fw_model)
-fw_model
 summary(fw_model)
@@
 
+```
+
+```{r}
 ols_plot_cooksd_bar(fw_model)
@@
 plot(fw_fit)
+
+```
+
+```{r}
+
+fw_predictions = c(predict(fw_model, newdata = one_encode_test_data_q2))
+
+fw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=fw_predictions)
+fw_submission
+write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")
 ```
@@
 bw_fit
+```
+
+```{r}
 bw_model = bw_fit$model
 ols_press(bw_model)
-bw_model
 summary(bw_model)
 confint(bw_model)
+```
 
+```{r}
 ols_plot_cooksd_bar(bw_model)
@@
 plot(bw_fit)
+```
+```{r}
 
+bw_predictions = c(predict(bw_model, newdata = one_encode_test_data_q2))
+bw_predictions
+
+bw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=bw_predictions)
+bw_submission
+write_csv(bw_submission, "../kaggleData/backwardsSelectionPredictions.csv")
 ```

### 2020-12-03 R - Deliverable/MSDS 6371 - Project.Rmd
some changes

@@
 stepwise_submission
-write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")
+#write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")
 ```
@@
 fw_submission
-write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")
+#write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")
 ```
@@
 bw_submission
-write_csv(bw_submission, "../kaggleData/backwardsSelectionPredictions.csv")
+#write_csv(bw_submission, "../kaggleData/backwardsSelectionPredictions.csv")
 ```

### 2020-12-03 R - Deliverable/MSDS 6371 - Project.Rmd
some changes

@@
 ```
+
+```{r message=FALSE, warning=FALSE}
+#Backward Selection
+custom_fit = ols_step_best_subset(lm_fit_q2,)
+custom_fit
+```
+
+```{r}
+custom_model = custom_fit$model
+ols_press(custom_model)
+summary(custom_model)
+confint(custom_model)
+```
+
+```{r}
+ols_plot_cooksd_bar(custom_model)
+
+custom_model_outliers = ols_plot_cooksd_bar(custom_model, print_plot=F)
+custom_model_outliers
+
+ols_plot_dffits(custom_model)
+ols_plot_diagnostics(custom_model)
+
+ols_plot_resid_fit(custom_model)
+ols_plot_resid_pot(custom_model)
+ols_pred_rsq(custom_model)
+plot(custom_fit)
+```
+
+```{r}
+
+custom_predictions = c(predict(custom_model, newdata = one_encode_test_data_q2))
+custom_predictions
+
+custom_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=custom_predictions)
+custom_submission
+#write_csv(custom_submission, "../kaggleData/customSelectionPredictions.csv")
+```

### 2020-12-03 R - Deliverable/MSDS 6371 - Project.Rmd
some changes

@@
 #Reference Neighborhood_BrkSide
-lm_fit_q1 = lm(SalePrice ~. -Id-Neighborhood_BrkSide+Neighborhood_Edwards*GrLivArea+Neighborhood_NAmes*GrLivArea, data = one_encode_train_data_q1)
+lm_fit_q1 = lm(SalePrice ~-Id- Neighborhood_BrkSide+ GrLivArea+Neighborhood_Edwards*GrLivArea+Neighborhood_NAmes*GrLivArea, data = one_encode_train_data_q1)
 

### 2020-12-03 R - Deliverable/MSDS 6371 - Project.Rmd
Fix Variable name
Initial Commit

--- 2020-12-03 R - Deliverable/MSDS 6371 - Project.Rmd
@@
 ```{r message=FALSE, warning=FALSE}
-library(olsrr)
 library(tidyverse)
@@
 data_train = as.data.frame(unclass(data_train))
+data_train$Neighborhood = as.factor(data_train$Neighborhood )
 data_test = as.data.frame(unclass(data_test))
-nrow(data_test)
+data_test$Neighborhood = as.factor(data_test$Neighborhood )
+head(data_train)
 ```
@@
 
-summary(lm_fit_experiment)
+#summary(lm_fit_experiment)
 #confint(lm_fit_experiment,  level=0.995)
@@
 ```{r message=FALSE, warning=FALSE}
-for (i in unlist(unique(data$Neighborhood)) ) {
-  print(scatter_func(data, i))
+for (i in unlist(unique(data_train$Neighborhood)) ) {
+  print(scatter_func(data_train, i))
 }
@@
 #Reference Neighborhood_BrkSide
-lm_fit_q1 = lm(SalePrice ~. -Id-Neighborhood_BrkSide+Neighborhood_Edwards*GrLivArea+Neighborhood_NAmes*GrLivArea, data = one_encode_train_data_q1)
+lm_fit_q1 = lm(SalePrice ~-Id- Neighborhood_BrkSide+ GrLivArea+Neighborhood_Edwards+Neighborhood_NAmes+ Neighborhood_Edwards*GrLivArea+Neighborhood_NAmes*GrLivArea, data = one_encode_train_data_q1)
 

### 2020-12-03 R - Deliverable/unit14/Untitled.Rmd
Initial Commit

---
title: "R Notebook"
output: html_notebook
---

This is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*.

```{r}
library(tidyverse)
library(olsrr)
```

```{r}
exclude_df = data.frame(x=c(1,2,3,4),y=c(2,3,3,3))
include_df = data.frame(x=c(1,2,3,4,30),y=c(2,3,3,3,50))
```

````{r}
exclude_fit = lm(y ~x, data=exclude_df)
summary(exclude_fit)
confint(exclude_fit)
ols_plot_cooksd_bar(exclude_fit)
ols_plot_diagnostics(exclude_fit)
```
````{r}
include_fit = lm(y ~x, data=include_df)
summary(include_fit)
confint(include_fit)
ols_plot_cooksd_bar(include_fit)
ols_plot_diagnostics(include_fit)
```
```{r warning=FALSE}
data = read_csv("/Users/dgrijalva/SMU/Classes/Term Fall 2020/Stats-Foundation/MSDS_6371_Stat_Foundations/Unit 14/SAT Data Set.csv")

```
```{r}
fit = lm (Expend ~.-State, data = data)

stepwise_fit = ols_step_both_p(fit, pent =0.05, prem=0.05,  details = F)
stepwise_fit
stepwise_model = stepwise_fit$model
ols_press(stepwise_model)
stepwise_model
summary(stepwise_model)
confint(stepwise_model)

ols_plot_cooksd_bar(stepwise_model)

stepwise_model_outliers = ols_plot_cooksd_bar(stepwise_model, print_plot=F)
stepwise_model_outliers

ols_plot_dffits(stepwise_model)
ols_plot_diagnostics(stepwise_model)

ols_plot_resid_fit(stepwise_model)
ols_plot_resid_pot(stepwise_model)
ols_pred_rsq(stepwise_model)
plot(stepwise_fit)

```

### 2020-12-04 R - Deliverable/MSDS 6371 - Project.Rmd
Add new models

@@
 data_test$Neighborhood = as.factor(data_test$Neighborhood )
-head(data_train)
+# add new remodel variable
+data_train$Remodel =ifelse(data_train$YearBuilt==data_train$YearRemodAdd, 0, 1)
+data_test$Remodel =ifelse(data_test$YearBuilt==data_test$YearRemodAdd, 0, 1)
+summary(data_train)
+summary(data_test)
+
 ```
@@
 test_data_q1 = data_test  %>% select(Id, GrLivArea, Neighborhood ) %>% filter(Neighborhood == "NAmes" | Neighborhood ==  "Edwards" | Neighborhood ==  "BrkSide") %>% droplevels()
-train_data_q1
-train_data_q2 = data_train %>% select(Id, GrLivArea, Neighborhood, SalePrice ) 
+
+train_data_q2 = data_train %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  SalePrice)
 train_data_q2$GrLivArea2 = train_data_q2$GrLivArea^2
 
-test_data_q2 = data_test %>% select(Id, GrLivArea, Neighborhood ) 
+# 2.5Fin does not exist in test data so changing it to 1.5Unf
+train_data_q2$HouseStyle = as.character(train_data_q2$HouseStyle)
+train_data_q2 = train_data_q2 %>%   mutate_at(vars(HouseStyle) ,     ~ifelse(.x=="2.5Fin","1.5Unf",.x  ))
+
+train_data_q2$HouseStyle = as.factor(train_data_q2$HouseStyle)
+
+test_data_q2 = data_test %>%  select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual,  YearRemodAdd, GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr, Remodel,OverallQual)
 test_data_q2$GrLivArea2 = test_data_q2$GrLivArea^2
-nrow(test_data_q2)
+
+test_data_q2$KitchenQual = as.character(test_data_q2$KitchenQual)
+test_data_q2 = test_data_q2 %>%   mutate_at(vars(KitchenQual) ,     ~ifelse(is.na(.x),"Ex",.x  ))
+test_data_q2$KitchenQual = as.factor(test_data_q2$KitchenQual)
+
+# Inpute = NA in test data
+test_data_q2= test_data_q2 %>% mutate_at(vars(GarageCars),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
+test_data_q2= test_data_q2 %>% mutate_at(vars(BsmtFullBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
+test_data_q2= test_data_q2 %>% mutate_at(vars(BsmtHalfBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
+
+summary(test_data_q2)
+#nrow(test_data_q2)
+unique(train_data_q2$HouseStyle)
+unique(test_data_q2$HouseStyle)
+```
+
+```{r}
+
+#look for missing values
+missing.values <- test_data_q2 %>%
+    gather(key = "key", value = "val") %>%
+    mutate(is.missing = is.na(val)) %>%
+    group_by(key, is.missing) %>%
+    summarise(num.missing = n()) %>%
+    filter(is.missing==T) %>%
+    select(-is.missing) %>%
+    arrange(desc(num.missing))
+
+missing.values
 ```
@@
 
+```{r}
+names(one_encode_train_data_q2)
+```
+
 #	ANALYSIS 2
@@
 one_encode_train_data_q2 =  one_hot(as.data.table(train_data_q2, dropUnusedLevels=TRUE))
+one_encode_train_data_q2
 one_encode_test_data_q2 =  one_hot(as.data.table(test_data_q2, dropUnusedLevels=TRUE))
-#lm_fit_q2 = lm(SalePrice ~. -Id-Neighborhood_BrkSide, data = one_encode_train_data_q2)
 
-#Neighborhood_Blmngtn
+#Refferences: Neighborhood_BrkSide KitchenQual_TA HouseStyle_SLvl SaleCondition_Partial
 
-lm_fit_q2 = lm(SalePrice ~.-GrLivArea2 -Id-Neighborhood_BrkSide+(Neighborhood_Blmngtn+Neighborhood_Blueste+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker)*GrLivArea, data = one_encode_train_data_q2)
+lm_fit_q2 = lm(SalePrice ~.-SaleCondition_Partial-Id-HouseStyle_SLvl-Neighborhood_BrkSide-KitchenQual_TA+
+
+                 (Neighborhood_Blmngtn+Neighborhood_Blueste+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd )*GrLivArea +
+
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd )*GrLivArea2 +
+
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd )*LotArea +
+
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd ) * BedroomAbvGr
+
+               , data = one_encode_train_data_q2)
 
@@
 stepwise_predictions = c(predict(stepwise_model, newdata = one_encode_test_data_q2))
+one_encode_test_data_q2[1117,]
 
 stepwise_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=stepwise_predictions)
-stepwise_submission
-#write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")
+
+write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")
+
+nrow(stepwise_submission)
+sum(is.na(stepwise_submission))
+stepwise_submission_na <- stepwise_submission %>% filter_all(any_vars(is.na(.))) 
+stepwise_submission_na
 ```
@@
 fw_submission
-#write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")
+write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")
+
+nrow(fw_submission)
+sum(is.na(fw_submission))
+fw_submission_na <- fw_submission %>% filter_all(any_vars(is.na(.))) 
+fw_submission_na
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-#Backward Selection
+
 bw_fit = ols_step_backward_p(lm_fit_q2, penter=0.05, details = F)
@@
 ```
+
 ```{r}
@@
 bw_submission
-#write_csv(bw_submission, "../kaggleData/backwardsSelectionPredictions.csv")
+write_csv(bw_submission, "../kaggleData/backwardsSelectionPredictions.csv")
+
+nrow(bw_submission)
+sum(is.na(bw_submission))
+bw_submission_na <- bw_submission %>% filter_all(any_vars(is.na(.))) 
+bw_submission_na
+
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-#Backward Selection
+
 custom_fit = ols_step_best_subset(lm_fit_q2,)
@@
 ```{r}
-custom_model = custom_fit$model
-ols_press(custom_model)
-summary(custom_model)
-confint(custom_model)
+#custom_model = custom_fit$model
+#ols_press(custom_model)
+#summary(custom_model)
+#confint(custom_model)
 ```
@@
 ```{r}
-ols_plot_cooksd_bar(custom_model)
+#ols_plot_cooksd_bar(custom_model)
 
-custom_model_outliers = ols_plot_cooksd_bar(custom_model, print_plot=F)
-custom_model_outliers
+#custom_model_outliers = ols_plot_cooksd_bar(custom_model, print_plot=F)
+#custom_model_outliers
 
-ols_plot_dffits(custom_model)
-ols_plot_diagnostics(custom_model)
+#ols_plot_dffits(custom_model)
+#ols_plot_diagnostics(custom_model)
 
-ols_plot_resid_fit(custom_model)
-ols_plot_resid_pot(custom_model)
-ols_pred_rsq(custom_model)
-plot(custom_fit)
+#ols_plot_resid_fit(custom_model)
+#ols_plot_resid_pot(custom_model)
+#ols_pred_rsq(custom_model)
+#plot(custom_fit)
 ```
@@
 
-custom_predictions = c(predict(custom_model, newdata = one_encode_test_data_q2))
-custom_predictions
+#custom_predictions = c(predict(custom_model, newdata = one_encode_test_data_q2))
+#custom_predictions
 
-custom_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=custom_predictions)
-custom_submission
+#custom_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=custom_predictions)
+#custom_submission
 #write_csv(custom_submission, "../kaggleData/customSelectionPredictions.csv")

### 2020-12-04 R - Deliverable/MSDS 6371 - Project.Rmd
add new models

@@
 library(olsrr)
+library(scales)
+library(caret)
 
@@
 train_data_q2$GrLivArea2 = train_data_q2$GrLivArea^2
+train_data_q2 = train_data_q2 %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  GrLivArea2, SalePrice)
 
@@
 
+train_data_q2_process = preProcess(train_data_q2[,2:20], method=c("center", "scale"))
+train_data_q2 =  predict(train_data_q2_process, train_data_q2)
+
 test_data_q2 = data_test %>%  select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual,  YearRemodAdd, GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr, Remodel,OverallQual)
 test_data_q2$GrLivArea2 = test_data_q2$GrLivArea^2
+test_data_q2 = test_data_q2 %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  GrLivArea2)
+test_data_q2 =  predict(train_data_q2_process, test_data_q2)
 
@@
 unique(test_data_q2$HouseStyle)
+
+```
+
+```{r}
+train_data_q2
+test_data_q2
 ```

### 2020-12-04 R - Deliverable/MSDS 6371 - Project.Rmd
add scaling and new variables to q2

@@
 data_test$Remodel =ifelse(data_test$YearBuilt==data_test$YearRemodAdd, 0, 1)
+data_train$GrLivArea2 = data_train$GrLivArea^2
+data_test$GrLivArea2 = data_test$GrLivArea^2
 summary(data_train)
@@
 
-train_data_q2 = data_train %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  SalePrice)
-train_data_q2$GrLivArea2 = train_data_q2$GrLivArea^2
-train_data_q2 = train_data_q2 %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  GrLivArea2, SalePrice)
+selected_features_q2 = c("GrLivArea", "Neighborhood", "LotArea", "YrSold", "SaleCondition", "HouseStyle", "KitchenQual", "YearRemodAdd","GarageCars", "PoolArea", "Fireplaces","BsmtFullBath","BsmtHalfBath","FullBath","HalfBath","BedroomAbvGr","Remodel","OverallQual", "GrLivArea2","X1stFlrSF","X2ndFlrSF","PoolArea")
+
+train_data_q2 = data_train %>% select(Id, selected_features_q2,  SalePrice)
 
@@
 
-test_data_q2 = data_test %>%  select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual,  YearRemodAdd, GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr, Remodel,OverallQual)
-test_data_q2$GrLivArea2 = test_data_q2$GrLivArea^2
-test_data_q2 = test_data_q2 %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  GrLivArea2)
+test_data_q2 = data_test %>%  select(Id, selected_features_q2)
 test_data_q2 =  predict(train_data_q2_process, test_data_q2)
@@
 #look for missing values
-missing.values <- test_data_q2 %>%
+missing.values <- train_data_q2 %>%
     gather(key = "key", value = "val") %>%
@@
 
-                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd )*GrLivArea2 +
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd)*GrLivArea2 +
 
-                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd )*LotArea +
-
-                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd ) * BedroomAbvGr
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer)*LotArea
 

### 2020-12-04 R - Deliverable/MSDS 6371 - Project.Rmd
Changes on the custom model

@@
 
-                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer)*LotArea
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer)*LotArea +
+
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd ) * BedroomAbvGr
 
@@
 ols_press(bw_model)
+formatC(ols_press(bw_model), format = "e", digits = 6)
 summary(bw_model)
@@
 ```
+```{r}
+custom_train_data_exclude
+
+```
+
+```{r}
+# outliers list
+ outliers_forward = c(4, 54,   59,   66,   67,   70,   94,  119,  121,  138,  152,  154,  164,  179,  186,  209,  219,  239,  250,  252,  262,  305,  314,  321,  322,  331,  336,  337,  349,  350,  363,  384,  385,  401,  427,  439,  441,  474,  478,  497,  524,  528,  530,  560,  567,  569,  582,  584,
+586,  589,  592,  598,  608,  622,  633,  636,  641,  643,  656,  662,  665,  682,  686,  689,  692,  703,  713,  725,  745,  770,  775,  779,  799,  804,  811,  813,  823,  826,  841,  876,  878,  886,  898,  899,  926,  940,  962,  971, 1018, 1025, 1032, 1045, 1047, 1049, 1063, 1066,
+1069, 1128, 1143, 1156, 1169, 1170, 1174, 1176, 1182, 1183, 1217, 1268, 1269, 1285, 1299, 1311, 1323, 1325, 1327, 1329, 1360, 1387, 1389, 1397, 1416, 1424, 1441)
+
+custom_train_data = data_train[!(data_train$Id %in% outliers_forward), ]
+
+#custom_train_data = data_train
+
+selected_features_q2 = c("GrLivArea", "Neighborhood", "LotArea", "YrSold", "SaleCondition", "HouseStyle", "KitchenQual", "YearRemodAdd","GarageCars", "PoolArea", "Fireplaces","BsmtFullBath","BsmtHalfBath","FullBath","HalfBath","BedroomAbvGr","Remodel","OverallQual", "GrLivArea2","X1stFlrSF","X2ndFlrSF","PoolArea")
+
+custom_train_data = custom_train_data %>% select(Id, selected_features_q2,  SalePrice)
+
+# 2.5Fin does not exist in test data so changing it to 1.5Unf
+custom_train_data$HouseStyle = as.character(custom_train_data$HouseStyle)
+custom_train_data = custom_train_data %>%   mutate_at(vars(HouseStyle) ,     ~ifelse(.x=="2.5Fin","1.5Unf",.x  ))
+
+custom_train_data$HouseStyle = as.factor(custom_train_data$HouseStyle)
+
+custom_train_data_process = preProcess(custom_train_data[,2:20], method=c("center", "scale"))
+custom_train_data =  predict(custom_train_data_process, custom_train_data)
+
+custom_test_data = data_test %>%  select(Id, selected_features_q2)
+custom_test_data =  predict(custom_train_data_process, test_data_q2)
+
+custom_test_data$KitchenQual = as.character(custom_test_data$KitchenQual)
+custom_test_data = custom_test_data %>%   mutate_at(vars(KitchenQual) ,     ~ifelse(is.na(.x),"Ex",.x  ))
+custom_test_data$KitchenQual = as.factor(custom_test_data$KitchenQual)
+
+# Inpute = NA in test data
+custom_test_data= custom_test_data %>% mutate_at(vars(GarageCars),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
+custom_test_data= custom_test_data %>% mutate_at(vars(BsmtFullBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
+custom_test_data= custom_test_data %>% mutate_at(vars(BsmtHalfBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
+
+one_encode_custom_train_data=  one_hot(as.data.table(custom_train_data, dropUnusedLevels=TRUE))
+
+one_encode_custom_test_data =  one_hot(as.data.table(custom_test_data, dropUnusedLevels=TRUE))
+
+#Refferences: Neighborhood_BrkSide KitchenQual_TA HouseStyle_SLvl SaleCondition_Partial
+
+lm_fit_custom = lm(SalePrice ~.-SaleCondition_Partial-Id-HouseStyle_SLvl-Neighborhood_BrkSide-KitchenQual_TA+
+
+                 (Neighborhood_Blmngtn+Neighborhood_Blueste+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd )*GrLivArea +
+
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd)*GrLivArea2 +
+
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer)*LotArea +
+
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd ) * BedroomAbvGr
+
+               , data = one_encode_custom_train_data)
+
+summary(lm_fit_custom)
+ols_press(lm_fit_custom)
+
+```
+
+```{r}
+
+one_encode_custom_train_data
+```
 
@@
 
-custom_fit = ols_step_best_subset(lm_fit_q2,)
+custom_fit = ols_step_forward_p(lm_fit_custom, penter=0.05, details = F)
 custom_fit
@@
 ```{r}
-#custom_model = custom_fit$model
-#ols_press(custom_model)
-#summary(custom_model)
-#confint(custom_model)
+custom_model = custom_fit$model
+ols_press(custom_model)
+formatC(ols_press(custom_model), format = "e", digits = 6)
+summary(custom_model)
+confint(custom_model)
 ```
@@
 ```{r}
-#ols_plot_cooksd_bar(custom_model)
+ols_plot_cooksd_bar(custom_model)
 
-#custom_model_outliers = ols_plot_cooksd_bar(custom_model, print_plot=F)
-#custom_model_outliers
+custom_model_outliers = ols_plot_cooksd_bar(custom_model, print_plot=F)
+custom_model_outliers
 
-#ols_plot_dffits(custom_model)
-#ols_plot_diagnostics(custom_model)
+ols_plot_dffits(custom_model)
+ols_plot_diagnostics(custom_model)
 
-#ols_plot_resid_fit(custom_model)
-#ols_plot_resid_pot(custom_model)
-#ols_pred_rsq(custom_model)
-#plot(custom_fit)
+ols_plot_resid_fit(custom_model)
+ols_plot_resid_pot(custom_model)
+ols_pred_rsq(custom_model)
+plot(custom_fit)
+```
+```{r}
+enco
+custom_model_outliers$outliers$observation
+
 ```
@@
 
-#custom_predictions = c(predict(custom_model, newdata = one_encode_test_data_q2))
-#custom_predictions
+custom_predictions = c(predict(custom_model, newdata = one_encode_custom_test_data))
+custom_predictions
 
-#custom_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=custom_predictions)
-#custom_submission
-#write_csv(custom_submission, "../kaggleData/customSelectionPredictions.csv")
+custom_submission = data.frame(Id= one_encode_custom_test_data$Id, SalePrice=custom_predictions)
+custom_submission
+write_csv(custom_submission, "../kaggleData/customSelection1Predictions.csv")
 ```
+
+```{r}
+
+one_encode_custom_train_data_model2 = one_encode_custom_train_data
+one_encode_custom_train_data_model2 =  one_encode_custom_train_data %>% mutate( index=row_number())
+
+custom_model_1_outliers = c(4,    6,   13,   28,   30,   55,   96,  106,  107,  135,  143,  157,  163,  183,  208,  215,  296,  302,  304,  347,  354,  357,  375,  384,  385,  387,  415,  421,  426,  434,  437,  443,  444,  464,  498,  504,  520,  525,  556,  587,  600,  603,  616,  618,  628,  636,  641,  652,
+ 661,  671,  679,  697,  736,  751,  770,  786,  813,  842,  877,  886,  887,  900,  903,  932,  941,  946,  950,  952,  976, 1001, 1004, 1030, 1033, 1047, 1058, 1064, 1065, 1069, 1079, 1117, 1120, 1124, 1133, 1137, 1138, 1144, 1147, 1173, 1204, 1229, 1234, 1240, 1245, 1265, 1267, 1270,
+1277, 1284, 1311)
+
+one_encode_custom_train_data_model2 = one_encode_custom_train_data_model2[!(one_encode_custom_train_data_model2$index %in% custom_model_1_outliers), ]
+one_encode_custom_train_data_model2
+
+#get original data again without all the outliers. This way we can scale it using only the values we will utilize, we do this to avoid data leaking
+final_one_encode_custom_train_data_model2 = data_train[(data_train$Id %in% one_encode_custom_train_data_model2$Id), ]
+final_one_encode_custom_train_data_model2
+```
+```{r}
+# do all the data preprossesing again
+
+final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>% select(Id, selected_features_q2,  SalePrice)
+
+# 2.5Fin does not exist in test data so changing it to 1.5Unf
+final_one_encode_custom_train_data_model2$HouseStyle = as.character(final_one_encode_custom_train_data_model2$HouseStyle)
+final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>%   mutate_at(vars(HouseStyle) ,     ~ifelse(.x=="2.5Fin","1.5Unf",.x  ))
+
+final_one_encode_custom_train_data_model2$HouseStyle = as.factor(final_one_encode_custom_train_data_model2$HouseStyle)
+
+custom2_train_data_process = preProcess(final_one_encode_custom_train_data_model2[,2:20], method=c("center", "scale"))
+final_one_encode_custom_train_data_model2 =  predict(custom2_train_data_process, final_one_encode_custom_train_data_model2)
+
+final_custom_test_data = data_test %>%  select(Id, selected_features_q2)
+final_custom_test_data =  predict(custom2_train_data_process, final_custom_test_data)
+
+final_custom_test_data$KitchenQual = as.character(final_custom_test_data$KitchenQual)
+final_custom_test_data = custom_test_data %>%   mutate_at(vars(KitchenQual) ,     ~ifelse(is.na(.x),"Ex",.x  ))
+final_custom_test_data$KitchenQual = as.factor(final_custom_test_data$KitchenQual)
+
+# Inpute = NA in test data
+final_custom_test_data= final_custom_test_data %>% mutate_at(vars(GarageCars),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
+final_custom_test_data= final_custom_test_data %>% mutate_at(vars(BsmtFullBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
+final_custom_test_data= final_custom_test_data %>% mutate_at(vars(BsmtHalfBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
+
+one_encode_custom_train_data2=  one_hot(as.data.table(final_one_encode_custom_train_data_model2, dropUnusedLevels=TRUE))
+
+one_encode_custom_test_data2 =  one_hot(as.data.table(final_custom_test_data, dropUnusedLevels=TRUE))
+
+#Refferences: Neighborhood_BrkSide KitchenQual_TA HouseStyle_SLvl SaleCondition_Partial
+# Manual exclusion:
+# take away PoolArea due to 0 variance warning
+#SaleCondition_AdjLand:GrLivArea2           NA         NA      NA       NA    
+#SaleCondition_Alloca:GrLivArea2            NA         NA      NA       NA 
+#LotArea:SaleCondition_AdjLand              NA         NA      NA       NA    
+#LotArea:SaleCondition_Alloca               NA         NA      NA       NA    
+#SaleCondition_Alloca:BedroomAbvGr          NA         NA      NA       NA
+
+lm_fit_custom2 = lm(SalePrice ~.-SaleCondition_Partial-Id-HouseStyle_SLvl-Neighborhood_BrkSide-KitchenQual_TA-PoolArea+
+
+                 (Neighborhood_Blmngtn+Neighborhood_Blueste+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd )*GrLivArea +
+
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd)*GrLivArea2 +
+
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml++SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer)*LotArea +
+
+                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd ) * BedroomAbvGr
+
+               , data = one_encode_custom_train_data2)
+
+summary(lm_fit_custom2)
+ols_press(lm_fit_custom2)
+
+```
+```{r message=FALSE, warning=FALSE}
+
+custom_fit2 = ols_step_forward_p(lm_fit_custom2, penter=0.05, details = F)
+custom_fit2
+```
+
+```{r}
+custom_model2 = custom_fit2$model
+ols_press(custom_model2)
+formatC(ols_press(custom_model2), format = "e", digits = 6)
+summary(custom_model2)
+confint(custom_model2)
+```
+
+```{r}
+ols_plot_cooksd_bar(custom_model2)
+
+custom_model_outliers2 = ols_plot_cooksd_bar(custom_model2, print_plot=F)
+custom_model_outliers2
+
+ols_plot_dffits(custom_model2)
+ols_plot_diagnostics(custom_model2)
+
+ols_plot_resid_fit(custom_model2)
+ols_plot_resid_pot(custom_model2)
+ols_pred_rsq(custom_model2)
+plot(custom_fit2)
+```
+
+```{r}
+
+custom_model_outliers2$outliers$observation
+
+```
+
+```{r}
+
+custom_predictions2 = c(predict(custom_model2, newdata = one_encode_custom_test_data2))
+custom_predictions2
+
+custom_predictions2 = data.frame(Id= one_encode_custom_test_data2$Id, SalePrice=custom_predictions2)
+custom_predictions2
+write_csv(custom_predictions2, "../kaggleData/customSelection2Predictions.csv")
+```

### 2020-12-05 R - Deliverable/MSDS 6371 - Project.Rmd
Changes on the custom model

@@
 final_custom_test_data$KitchenQual = as.character(final_custom_test_data$KitchenQual)
-final_custom_test_data = custom_test_data %>%   mutate_at(vars(KitchenQual) ,     ~ifelse(is.na(.x),"Ex",.x  ))
+final_custom_test_data = final_custom_test_data %>%   mutate_at(vars(KitchenQual) ,     ~ifelse(is.na(.x),"Ex",.x  ))
 final_custom_test_data$KitchenQual = as.factor(final_custom_test_data$KitchenQual)
@@
 custom_predictions2 = c(predict(custom_model2, newdata = one_encode_custom_test_data2))
-custom_predictions2
 
@@
 ```
+```{r}
+one_encode_custom_test_data2
+```
+```{r}
+custom_model2
+
+```

### 2020-12-05 R - Deliverable/MSDS 6371 - Project.Rmd
fix: as.factor on necessary categorical variables

@@
 data_train = as.data.frame(unclass(data_train))
-data_train$Neighborhood = as.factor(data_train$Neighborhood )
+data_train$Neighborhood = as.factor(data_train$Neighborhood)
+data_train$HouseStyle = as.factor(data_train$HouseStyle)
+data_train$KitchenQual = as.factor(data_train$KitchenQual)
+data_train$SaleCondition = as.factor(data_train$SaleCondition)
+
 data_test = as.data.frame(unclass(data_test))
 data_test$Neighborhood = as.factor(data_test$Neighborhood )
+data_test$HouseStyle = as.factor(data_test$HouseStyle)
+data_test$KitchenQual = as.factor(data_test$KitchenQual)
+data_test$SaleCondition = as.factor(data_test$SaleCondition)
 # add new remodel variable
@@
 summary(data_test)
+head(data_train)
 

### 2020-12-06 R - Deliverable/MSDS-6371---Project.Rmd
final changes

--- 2020-12-05 R - Deliverable/MSDS 6371 - Project.Rmd
@@
 library(caret)
-
+library(dataPreparation)
+library(regclass)
 # options
@@
 data_test$GrLivArea2 = data_test$GrLivArea^2
-summary(data_train)
-summary(data_test)
+dim(data_train)
+dim(data_test)
+
+```
+
+```{r}
+ # In this function we will handle missing values ffor numerical and factor columns 
+impute_missing_values_func = function(data){
+
+  # create list of  Numerical Columns names
+    nums_col = data %>% purrr::discard(~!is.numeric(.)) %>% names
+
+    # create list of  factor Columns names
+    char_col = data %>% purrr::discard(~!is.character(.)) %>% names
+
+    # Create a new dataframe for q2 train data, this is a copy of the original train DF
+    treated_data = data
+
+    # Input NA's in numerical columns with the mediam value per column
+    for (i in nums_col){
+     treated_data = treated_data %>% mutate_at(vars(UQ(as.name(i))),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
+    }
+
+    # Create a new factor level called None for each NA in factor columns
+    for (i in char_col){
+      treated_data[i][is.na(treated_data[i])] = "None"
+    }
+
+    return(treated_data)
+
+}
+
+show_missing_values = function(data){
+      missing.values <- data %>%
+        gather(key = "key", value = "val") %>%
+        mutate(is.missing = is.na(val)) %>%
+        group_by(key, is.missing) %>%
+        summarise(num.missing = n()) %>%
+        filter(is.missing==T) %>%
+        select(-is.missing) %>%
+        arrange(desc(num.missing))
+
+    print(missing.values$key)
+
+}
+
+```
+
+```{r message=FALSE, warning=FALSE}
+# Let's handle the missing values
+# show missing values on train DF
+
+#show_missing_values(data_train)
+#show_missing_values(data_test)
+#data_train_q2 = impute_missing_values_func(data_train)
+#data_test_q2 = impute_missing_values_func(data_test)
+
+# show missing values on treated train DF - there should be 0
+#show_missing_values(data_train_q2)
+#show_missing_values(data_test_q2)
+
+```
+
+```{r}
+
+#encoding = build_encoding(data_set = data_train_q2, cols = "auto", verbose = TRUE)
+#enconded_data_train_q2 = one_hot_encoder(data_set = data_train_q2, encoding = encoding, drop = TRUE, verbose = F)
+#enconded_data_test_q2 = one_hot_encoder(data_set = data_test_q2, encoding = encoding, drop = TRUE, verbose = F)
+#print(dim(enconded_data_train_q2))
+#print(dim(enconded_data_test_q2))
 
@@
 train_data_q2 = train_data_q2 %>%   mutate_at(vars(HouseStyle) ,     ~ifelse(.x=="2.5Fin","1.5Unf",.x  ))
-
 train_data_q2$HouseStyle = as.factor(train_data_q2$HouseStyle)
 
-train_data_q2_process = preProcess(train_data_q2[,2:20], method=c("center", "scale"))
+train_data_q2_process = preProcess(train_data_q2[,2:22], method=c("center", "scale"))
 train_data_q2 =  predict(train_data_q2_process, train_data_q2)
@@
 
-# Inpute = NA in test data
+# Impute = NA in test data
 test_data_q2= test_data_q2 %>% mutate_at(vars(GarageCars),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
@@
 summary(test_data_q2)
-#nrow(test_data_q2)
+nrow(test_data_q2)
 unique(train_data_q2$HouseStyle)
@@
 
-```{r}
-train_data_q2
-test_data_q2
-```
-
-```{r}
-
-#look for missing values
-missing.values <- train_data_q2 %>%
-    gather(key = "key", value = "val") %>%
-    mutate(is.missing = is.na(val)) %>%
-    group_by(key, is.missing) %>%
-    summarise(num.missing = n()) %>%
-    filter(is.missing==T) %>%
-    select(-is.missing) %>%
-    arrange(desc(num.missing))
-
-missing.values
-```
-
-```{r}
-
-#lm_fit_experiment = lm(SalePrice ~.
--Id-Utilities-Street-PoolQC-MiscFeature-Alley-Fence-FireplaceQu-LotFrontage-GarageCond-GarageFinish-GarageQual-GarageType-GarageYrBlt-BsmtExposure-BsmtFinType2-BsmtCond-BsmtFinType1-BsmtQual-MasVnrArea-MasVnrType-Electrical  , data = train)
-#lm_fit_experiment
-#Neighborhood_Blmngtn
-
-#summary(lm_fit_experiment)
-#confint(lm_fit_experiment,  level=0.995)
-
-```
+`
 
@@
 
-```{r}
-names(one_encode_train_data_q2)
-```
-
 #	ANALYSIS 2
 ```{r message=FALSE, warning=FALSE}
-
 one_encode_train_data_q2 =  one_hot(as.data.table(train_data_q2, dropUnusedLevels=TRUE))
@@
 
+# lm_fit_q2 = lm(SalePrice ~.-Id
+#               - SaleCondition.Family  
+# -SaleType.Oth
+# -MiscFeature.TenC 
+# -Fence.MnWw 
+# -PoolQC.Gd 
+# -PavedDrive.P
+# -GarageCond.Ex
+# -GarageCond.None
+# -GarageQual.Po
+# -GarageFinish.Fin 
+# -GarageType.CarPort
+# -FireplaceQu.Po  
+# -Functional.Sev 
+# -KitchenQual.Fa
+# -Electrical.None 
+# -CentralAir.N 
+# -HeatingQC.Po
+# -Heating.Floor
+# -BsmtFinType2.GLQ 
+# -BsmtFinType1.LwQ  
+# -BsmtExposure.None 
+# -BsmtCond.Po  
+# -BsmtCond.None
+# -BsmtQual.Fa 
+# -Foundation.Stone 
+# -ExterCond.Ex  
+# -ExterQual.Fa 
+# -MasVnrType.BrkCmn
+# -Exterior2nd.CBlock 
+# -Exterior1st.CBlock
+# -RoofMatl.ClyTile
+# -RoofStyle.Shed  
+# -HouseStyle.2.5Fin 
+# -BldgType.Twnhs
+# -Condition2.RRAe 
+# -Condition1.RRNe 
+# -Neighborhood.Blueste
+# -MSZoning.RH
+# -Alley.Pave 
+# -Utilities.NoSeWa 
+# -LotConfig.FR3 
+# -LandSlope.Sev
+# -Street.Grvl
+# , enconded_data_train_q2)
+
 summary(lm_fit_q2)
-confint(lm_fit_q2,  level=0.995)
 ```
+
 ## Model Selection
@@
 
-write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")
+#write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")
 
@@
 stepwise_submission_na
+```
+```{r}
+step_wise_vif = VIF(stepwise_model)
+step_wise_vif
 ```
@@
 summary(fw_model)
-confint(fw_model)
+#confint(fw_model)
 
@@
 fw_submission
-write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")
+#write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")
 
@@
 fw_submission_na
+```
+```{r}
+fw_vif = VIF(fw_model)
+c(fw_vif)
+
 ```
@@
 summary(bw_model)
-confint(bw_model)
+#confint(bw_model)
 ```
@@
 bw_submission
-write_csv(bw_submission, "../kaggleData/backwardsSelectionPredictions.csv")
+#write_csv(bw_submission, "../kaggleData/backwardsSelectionPredictions.csv")
 
@@
 ```{r}
-custom_train_data_exclude
+bw_vif = VIF(bw_model)
+c(bw_vif)
 
+```
+
+```{r}
+custom_train_data
+train_data_q2
 ```
@@
  1069, 1128, 1143, 1156, 1169, 1170, 1174, 1176, 1182, 1183, 1217, 1268, 1269, 1285, 1299, 1311, 1323, 1325, 1327, 1329, 1360, 1387, 1389, 1397, 1416, 1424, 1441)
+#outliers_forward = c(1047,770,1047,1424)
 
@@
 
-#custom_train_data = data_train
-
-selected_features_q2 = c("GrLivArea", "Neighborhood", "LotArea", "YrSold", "SaleCondition", "HouseStyle", "KitchenQual", "YearRemodAdd","GarageCars", "PoolArea", "Fireplaces","BsmtFullBath","BsmtHalfBath","FullBath","HalfBath","BedroomAbvGr","Remodel","OverallQual", "GrLivArea2","X1stFlrSF","X2ndFlrSF","PoolArea")
+selected_features_q2 = c("GrLivArea", "Neighborhood", "LotArea", "YrSold", "SaleCondition", "HouseStyle", "KitchenQual", "YearRemodAdd","GarageCars", "Fireplaces","BsmtFullBath","BsmtHalfBath","FullBath","HalfBath","BedroomAbvGr","Remodel","OverallQual", "GrLivArea2","X1stFlrSF","X2ndFlrSF","PoolArea")
 
@@
 
-custom_train_data_process = preProcess(custom_train_data[,2:20], method=c("center", "scale"))
+custom_train_data_process = preProcess(custom_train_data[,2:22], method=c("center", "scale"))
 custom_train_data =  predict(custom_train_data_process, custom_train_data)
@@
 custom_test_data = data_test %>%  select(Id, selected_features_q2)
-custom_test_data =  predict(custom_train_data_process, test_data_q2)
+custom_test_data =  predict(custom_train_data_process, custom_test_data)
 
@@
 ```{r}
+#custom_train_data
 
-one_encode_custom_train_data
 ```
@@
 summary(custom_model)
-confint(custom_model)
+#confint(custom_model)
 ```
@@
 ```{r}
-enco
 custom_model_outliers$outliers$observation
@@
 custom_submission
-write_csv(custom_submission, "../kaggleData/customSelection1Predictions.csv")
+#write_csv(custom_submission, "../kaggleData/customSelection3Predictions.csv")
 ```
@@
 
+custom1_vif = VIF(custom_model)
+c(custom1_vif)
+```
+
+```{r}
+one_encode_custom_train_data_model2
+
+```
+
+```{r}
 one_encode_custom_train_data_model2 = one_encode_custom_train_data
-one_encode_custom_train_data_model2 =  one_encode_custom_train_data %>% mutate( index=row_number())
 
-custom_model_1_outliers = c(4,    6,   13,   28,   30,   55,   96,  106,  107,  135,  143,  157,  163,  183,  208,  215,  296,  302,  304,  347,  354,  357,  375,  384,  385,  387,  415,  421,  426,  434,  437,  443,  444,  464,  498,  504,  520,  525,  556,  587,  600,  603,  616,  618,  628,  636,  641,  652,
- 661,  671,  679,  697,  736,  751,  770,  786,  813,  842,  877,  886,  887,  900,  903,  932,  941,  946,  950,  952,  976, 1001, 1004, 1030, 1033, 1047, 1058, 1064, 1065, 1069, 1079, 1117, 1120, 1124, 1133, 1137, 1138, 1144, 1147, 1173, 1204, 1229, 1234, 1240, 1245, 1265, 1267, 1270,
-1277, 1284, 1311)
+one_encode_custom_train_data_model2$index = seq.int(nrow(one_encode_custom_train_data_model2))
+one_encode_custom_train_data_model2
 
+ custom_model_1_outliers = c( 556)
+#
+#
+#
  one_encode_custom_train_data_model2 = one_encode_custom_train_data_model2[!(one_encode_custom_train_data_model2$index %in% custom_model_1_outliers), ]
  one_encode_custom_train_data_model2
-
+#
+#
 #get original data again without all the outliers. This way we can scale it using only the values we will utilize, we do this to avoid data leaking
@@
 ```
+
 ```{r}
 # do all the data preprossesing again
-
 final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>% select(Id, selected_features_q2,  SalePrice)
 
-# 2.5Fin does not exist in test data so changing it to 1.5Unf
+# # 2.5Fin does not exist in test data so changing it to 1.5Unf
 final_one_encode_custom_train_data_model2$HouseStyle = as.character(final_one_encode_custom_train_data_model2$HouseStyle)
@@
 
-custom2_train_data_process = preProcess(final_one_encode_custom_train_data_model2[,2:20], method=c("center", "scale"))
+custom2_train_data_process = preProcess(final_one_encode_custom_train_data_model2[,2:22], method=c("center", "scale"))
 final_one_encode_custom_train_data_model2 =  predict(custom2_train_data_process, final_one_encode_custom_train_data_model2)
@@
 
-# Inpute = NA in test data
+#  Impute = NA in test data
 final_custom_test_data= final_custom_test_data %>% mutate_at(vars(GarageCars),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
@@
 
-#Refferences: Neighborhood_BrkSide KitchenQual_TA HouseStyle_SLvl SaleCondition_Partial
-# Manual exclusion:
-# take away PoolArea due to 0 variance warning
-#SaleCondition_AdjLand:GrLivArea2           NA         NA      NA       NA    
-#SaleCondition_Alloca:GrLivArea2            NA         NA      NA       NA 
-#LotArea:SaleCondition_AdjLand              NA         NA      NA       NA    
-#LotArea:SaleCondition_Alloca               NA         NA      NA       NA    
-#SaleCondition_Alloca:BedroomAbvGr          NA         NA      NA       NA
+# #References: Neighborhood_BrkSide KitchenQual_TA HouseStyle_SLvl SaleCondition_Partial
+# # Manual exclusion:
+# # take away PoolArea due to 0 variance warning
+# #SaleCondition_AdjLand:GrLivArea2           NA         NA      NA       NA
+# #SaleCondition_Alloca:GrLivArea2            NA         NA      NA       NA
+# #LotArea:SaleCondition_AdjLand              NA         NA      NA       NA
+# #LotArea:SaleCondition_Alloca               NA         NA      NA       NA
+# #SaleCondition_Alloca:BedroomAbvGr          NA         NA      NA       NA
 
@@
 summary(lm_fit_custom2)
+
 ols_press(lm_fit_custom2)
@@
 ```
+
 ```{r message=FALSE, warning=FALSE}
@@
 summary(custom_model2)
-confint(custom_model2)
+# confint(custom_model2)
 ```
@@
  ols_plot_cooksd_bar(custom_model2)
-
+# 
 custom_model_outliers2 = ols_plot_cooksd_bar(custom_model2, print_plot=F)
 custom_model_outliers2
-
+# 
 ols_plot_dffits(custom_model2)
 ols_plot_diagnostics(custom_model2)
-
+# 
 ols_plot_resid_fit(custom_model2)
@@
 
-custom_model_outliers2$outliers$observation
+# custom_model_outliers2$outliers$observation
 
@@
 custom_predictions2 = c(predict(custom_model2, newdata = one_encode_custom_test_data2))
-
+# 
+# 
 custom_predictions2 = data.frame(Id= one_encode_custom_test_data2$Id, SalePrice=custom_predictions2)
 custom_predictions2
-write_csv(custom_predictions2, "../kaggleData/customSelection2Predictions.csv")
+#write_csv(custom_predictions2, "../kaggleData/customSelection4Predictions.csv")
 ```
 ```{r}
-one_encode_custom_test_data2
+
+custom2_vif = VIF(custom_model2)
+c(custom2_vif)
+```
+
+```{r}
+#custom_model2$terms
+
+```
+
+```{r}
+
+#custom_fit3 = ols_step_both_p(lm_fit_custom2, penter=0.05, details = F)
+# OverallQual        X1stFlrSF  HouseStyle_2Story  GrLivArea    KitchenQual_Gd:GrLivArea   GrLivArea2:KitchenQual_Gd
+
+lm_fit_custom3 = lm(SalePrice ~ OverallQual  + GarageCars + 
+    BsmtFullBath + KitchenQual_Ex + YearRemodAdd + Neighborhood_OldTown + 
+    LotArea + GrLivArea:KitchenQual_Gd + Neighborhood_Crawfor + 
+    Neighborhood_NridgHt + SaleCondition_Abnorml + Neighborhood_Somerst + 
+    HalfBath + Neighborhood_Edwards + SaleCondition_Normal + 
+    SaleCondition_Alloca + BsmtHalfBath + FullBath + Neighborhood_ClearCr + 
+    Neighborhood_MeadowV + Neighborhood_SawyerW + Neighborhood_Mitchel + 
+    Neighborhood_BrDale + SaleCondition_Family + SaleCondition_AdjLand + 
+    Neighborhood_IDOTRR + YrSold + Neighborhood_NPkVill + HouseStyle_SFoyer + 
+    Neighborhood_Timber + KitchenQual_Fa + Neighborhood_Sawyer + 
+     Neighborhood_Blueste + Fireplaces + Neighborhood_Blmngtn + 
+    Neighborhood_CollgCr + Neighborhood_Gilbert + Neighborhood_Veenker + 
+    Neighborhood_StoneBr + HouseStyle_1.5Unf + Remodel + Neighborhood_SWISU + 
+    HouseStyle_1.5Fin + BedroomAbvGr + HouseStyle_1Story + HouseStyle_2.5Unf + 
+     Neighborhood_NWAmes + KitchenQual_Gd +  
+    Neighborhood_NAmes + Neighborhood_NAmes:GrLivArea2 + Neighborhood_NoRidge + 
+    Neighborhood_OldTown:GrLivArea2  + 
+    Neighborhood_NridgHt:LotArea + Neighborhood_NridgHt:BedroomAbvGr + 
+    Neighborhood_Somerst:GrLivArea2 + Neighborhood_StoneBr:GrLivArea2 + 
+    HouseStyle_1Story:GrLivArea2 + GrLivArea:Neighborhood_Sawyer + 
+    Neighborhood_Edwards:GrLivArea2 + LotArea:SaleCondition_Abnorml + 
+    LotArea:HouseStyle_1Story + KitchenQual_Ex:BedroomAbvGr + 
+    KitchenQual_Gd:BedroomAbvGr + Neighborhood_Somerst:LotArea + 
+    Neighborhood_Edwards:LotArea + Neighborhood_Veenker:BedroomAbvGr + 
+     Neighborhood_NAmes:BedroomAbvGr + 
+    SaleCondition_Family:BedroomAbvGr + Neighborhood_CollgCr:BedroomAbvGr + 
+    Neighborhood_StoneBr:LotArea + Neighborhood_Timber:GrLivArea2 + 
+    Neighborhood_Timber:BedroomAbvGr
+                , data = one_encode_custom_train_data2)
+summary(lm_fit_custom3)
+formatC(ols_press(lm_fit_custom3), format = "e", digits = 6)
+```
+
+```{r}
+ ols_plot_cooksd_bar(lm_fit_custom3)
+# 
+custom_model_outliers3 = ols_plot_cooksd_bar(lm_fit_custom3, print_plot=F)
+custom_model_outliers3
+# 
+ols_plot_dffits(lm_fit_custom3)
+#ols_plot_diagnostics(lm_fit_custom3)
+# 
+ols_plot_resid_fit(lm_fit_custom3)
+ols_plot_resid_pot(lm_fit_custom3)
+ols_pred_rsq(lm_fit_custom3)
+plot(lm_fit_custom3)
+```
+
+```{r}
+
+custom_predictions3 = c(predict(lm_fit_custom3, newdata = one_encode_custom_test_data2))
+# 
+# 
+custom_predictions3 = data.frame(Id= one_encode_custom_test_data2$Id, SalePrice=custom_predictions3)
+custom_predictions3
+write_csv(custom_predictions3, "../kaggleData/customSelection5Predictions.csv")
 ```
 ```{r}
-custom_model2
 
+custom3_vif = VIF(lm_fit_custom3)
+c(custom3_vif)
 ```

### 2020-12-07 R - Deliverable/MSDS 6371 - Project.Rmd
add knit code

--- 2020-12-05 R - Deliverable/MSDS 6371 - Project.Rmd
@@
 stepwise_submission_na <- stepwise_submission %>% filter_all(any_vars(is.na(.))) 
-stepwise_submission_na
+#stepwise_submission_na
+```
+```{r}
+step_wise_vif = VIF(stepwise_model)
+step_wise_vif
 ```
@@
 fw_submission_na <- fw_submission %>% filter_all(any_vars(is.na(.))) 
-fw_submission_na
+#fw_submission_na
+```
+```{r}
+fw_vif = VIF(fw_model)
+c(fw_vif)
+
 ```
@@
 ```{r}
-custom_train_data_exclude
+bw_vif = VIF(bw_model)
+c(bw_vif)
 
@@
 
-one_encode_custom_train_data
+custom_train_data_outliers = data_train[(data_train$Id %in% outliers_forward), ]
+#custom_train_data_outliers
+hist(custom_train_data_outliers$SalePrice)
+hist(one_encode_custom_train_data$SalePrice)
 ```
@@
 ```
+```{r}
+outliers_forward
 
+```
 ```{r}
@@
 custom_predictions = c(predict(custom_model, newdata = one_encode_custom_test_data))
-custom_predictions
+#custom_predictions
 
 custom_submission = data.frame(Id= one_encode_custom_test_data$Id, SalePrice=custom_predictions)
-custom_submission
-write_csv(custom_submission, "../kaggleData/customSelection1Predictions.csv")
+#custom_submission
+#write_csv(custom_submission, "../kaggleData/customSelection3Predictions.csv")
 ```
@@
 
+custom1_vif = VIF(custom_model)
+c(custom1_vif)
+```
+
+```{r}
+#one_encode_custom_train_data_model2
+
+```
+
+```{r}
 one_encode_custom_train_data_model2 = one_encode_custom_train_data
-one_encode_custom_train_data_model2 =  one_encode_custom_train_data %>% mutate( index=row_number())
 
-custom_model_1_outliers = c(4,    6,   13,   28,   30,   55,   96,  106,  107,  135,  143,  157,  163,  183,  208,  215,  296,  302,  304,  347,  354,  357,  375,  384,  385,  387,  415,  421,  426,  434,  437,  443,  444,  464,  498,  504,  520,  525,  556,  587,  600,  603,  616,  618,  628,  636,  641,  652,
- 661,  671,  679,  697,  736,  751,  770,  786,  813,  842,  877,  886,  887,  900,  903,  932,  941,  946,  950,  952,  976, 1001, 1004, 1030, 1033, 1047, 1058, 1064, 1065, 1069, 1079, 1117, 1120, 1124, 1133, 1137, 1138, 1144, 1147, 1173, 1204, 1229, 1234, 1240, 1245, 1265, 1267, 1270,
-1277, 1284, 1311)
+one_encode_custom_train_data_model2$index = seq.int(nrow(one_encode_custom_train_data_model2))
+#one_encode_custom_train_data_model2
 
+ custom_model_1_outliers = c( 556)
+#
+#
+#
  one_encode_custom_train_data_model2 = one_encode_custom_train_data_model2[!(one_encode_custom_train_data_model2$index %in% custom_model_1_outliers), ]
-one_encode_custom_train_data_model2
 
+ # one_encode_custom_train_data_model2
+#
+#
 #get original data again without all the outliers. This way we can scale it using only the values we will utilize, we do this to avoid data leaking
  final_one_encode_custom_train_data_model2 = data_train[(data_train$Id %in% one_encode_custom_train_data_model2$Id), ]
-final_one_encode_custom_train_data_model2
+ #final_one_encode_custom_train_data_model2
 ```
+
 ```{r}
 # do all the data preprossesing again
-
 final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>% select(Id, selected_features_q2,  SalePrice)
 
-# 2.5Fin does not exist in test data so changing it to 1.5Unf
+# # 2.5Fin does not exist in test data so changing it to 1.5Unf
 final_one_encode_custom_train_data_model2$HouseStyle = as.character(final_one_encode_custom_train_data_model2$HouseStyle)
